\cleardoublepage
\chapter*{Abstract} % The asterisk leaves out this chapter from the table of contents
A study of the AK-MCS method is presented, which seeks to optimize the determination of failure probabilities by means of Monte Carlo Simulations. A review of key concepts of structural reliability is made, in order to contextualize the field of application of the studied algorithm. A theoretical review of the Gaussian Process Regression is made to be able to understand the AK-MCS algorithm. Finally, several models are implemented, comparing the performance of AK-MCS with that of classical Monte Carlo Simulations. \\

\textbf{Keywords:} Monte Carlo Simulation, Structural Reliability Analysis, Krigin Regression, Active learning methods.

\cleardoublepage
\chapter*{Resumen} % The asterisk leaves out this chapter from the table of contents
Se presenta un estudio del método AK-MCS, el cual busca optimizar la determinación de probabilidades de falla mediante las Simulaciones de Monte Carlo. Se hace una revisión de conceptos clave de confiabilidad estructural, con el fin de contextualizar el campo de aplicación del algoritmo estudiado. Para poder entender AK-MCS, se hace una revisión teórica de las regresiones mediante procesos gaussianos. Finalmente, se implementan varios modelos, comparando el desempeño del algoritmo estudiado, con el de las simulaciones de Monte Carlo clásicas. \\

 \textbf{Palabras clave:} Simulación de Monte Carlo, Análisis de confiabilidad estructural, Regresión Kriging, Métodos de aprendizaje activo.